Object-Oriented Internet - Azure Interoperability

### 2020-11-29 Latex/Manuscript.tex
Work out Markdown\70.Conclusion.md #36
- fixes #36

Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology. It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems(CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e. Industry 4.0 (I4.0) and the Internet of Things (IoT) (Sect. \ref*{introduction}).

CPS is composed using the multi-vendor components interconnected atop of the Machine To Machine (M2M) communication. In many applications, the dynamic nature of the CPS must be considered. Dynamic nature means that interconnected assets may be added/removed from the network at any time. By design, CPS typically must fulfill the real-time and assets mobility requirements.

@@

This paper has presented a new generic architecture applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.

@@

To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect. \ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect. \ref*{introduction}) concept. We proposed to use an open-source library named \textit{emph.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose. It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.

We derived the final model presented in Fig. \ref*{figure3.ImplementationDomainModel} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig. \ref*{figure1.StrategyDomainModel}). In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role implemented as as a composable part aggregated by the \textit{Reactive Application}.

@@

The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. It is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. In the proposed approach the cloud interoperability is obtained by implementation only a dedicated part employing out-of-band communication without dependency on the OPC UA implementation. It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills. Because the part is composed at run-time it makes it possible to modify its functionality later after releasing the library or deploying the application program in the production environment.

Concluding, the paper describes a proof of the concept that applying the proposed architecture and implementation scenario it is possible to interconnect selected cloud services (e.g. \textbf{Azure\ Industrial\ IoT}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub. It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data export out of the OPC UA ecosystem functionality.

>>>>

Nowadays, the macro optimization of the industrial processes requires an integration of a vast variety of distributed applications provided by the Information and Communication Technology. It requires further research on the integration of \textbf{machine-centric} Cyber-Physical Systems (CPS) with \textbf{human-centric} front-end in the context of new emerging disciplines, i.e. Industry 4.0 (I4.0) and the Internet of Things (IoT) (Sect. \ref*{introduction}).

CPS is composed using the multi-vendor components (data holding assets) interconnected atop of the Machine To Machine (M2M) communication. In many applications, the dynamic nature of the CPS must be considered. Dynamic nature means that interconnected assets may be added/removed from the network at any time. By design, typically CPS must fulfill the real-time and mobility of the assets requirements.

@@

The main goal of this research is working out a new generic architecture and deployment scenario applicable for the integration of the \textbf{machine-centric} CPS and emerging cloud computing as a \textbf{human-centric} front-end.

@@

To promote interoperability and address the demands of the M2M communication in the context of a multi-vendor environment the prototyping should use a framework that must be compliant with the OPC UA Part 14 PubSub (Sect. \ref*{subs.architecture}) and support the \emph{Reactive Interoperability} (Sect. \ref*{introduction}) concept. We proposed to use an open-source library named \emph{UAOOI.Networking} (\emph{Networking} for short) (Fig.~\ref*{figure2.UADataApplicationArchitecture}) for this purpose. It is worth stressing that based on this approach only dedicated functionality related to the communication with the cloud must be implemented.

We derived the final model presented in Fig. \ref*{figure4.ImplementationArchitecture} by merging selected entities from the \emph{Networking} library (Fig.~\ref*{figure2.UADataApplicationArchitecture}) into the generic interconnection domain model (Fig. \ref*{figure1.StrategyDomainModel}). In the proposed approach the \textit{Embedded Gateway} is derived from the \textit{Consumer} role implemented as as a composable part aggregated by the \textit{Reactive Application}.

@@

The described results prove that the \textbf{embedded gateway} archetype implementation is possible based on the existing standalone framework supporting reactive interoperability atop of the M2M communication compliant with the OPC UA PubSub standard. It is worth stressing that there is no dependency on the Client/Server session-oriented relationship. This relationship is in contrast to the architecture described in the OPC UA Part 1 \cite{OPCUAPart1} specification where the publisher role is tightly coupled with the \textbf{Address Space} embedded component of the OPC UA Server. In the proposed approach the cloud interoperability is obtained by implementing a dedicated part employing out-of-band communication only without dependency on the OPC UA functionality at all. It is worth stressing that the gateway functionality is implemented as a part - composable to the whole without programming skills. Because the part is composed at the runtime it makes it possible to modify its functionality later after releasing the library or even deploying the application program in the production environment.

Concluding, the paper describes a proof of the concept that applying the proposed architecture and deployment scenario it is possible to interconnect selected cloud services (e.g. \textbf{Azure\ Industrial\ IoT}) with the \emph{Cyber-physical network} interconnected as one whole atop of the OPC UA PubSub. It is in contrast to interconnecting cloud services with the selected \emph{ Address\ Space} exposed by a selected OPC UA server limiting the PubSub role to data exporter transferring the data out of the OPC UA ecosystem.
